Stats

### 2022-03-18 stats/analysis.Rmd
for corr plots: color according to age group

```{r variation_hedge_plot}
hedge_variation_plot <- ggplot() +
  # child data
  geom_smooth(
    data = variationHedgeInd %>% filter(sample == "kids"),  
    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
    method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey",
  ) +

@@

  # adult data
  geom_jitter(
    data = variationHedgeInd %>% filter(sample == "adults"), 
    aes(x = 6.5, y = mean, shape = datacollection), alpha = .15, width = .05, height = .01,  
  ) +

@@

  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) +

@@

```{r intCon_hedge_data}
# take data of first reli day for internal consistency
hedge_intCon <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  # group_by(subjID, targetPosition, sample) %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample) %>%
  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)

@@

```{r intCon_hedge_kids}
hedge_intCon_kids <- hedge_intCon %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "#006c66", size = 0.7) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 5, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r intCon_hedge_adults}
hedge_intCon_adults <- hedge_intCon %>% 
  filter(sample == "adults") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 2, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r intCon_box_data}
# take data of first reli day for internal consistency
box_intCon <- reli %>% 
  filter(studyversion == "box" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample) %>%
  tidyboot_mean(column = correctBox, na.rm = TRUE)

@@

```{r intCon_box_kids}
box_intCon_kids <- box_intCon %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "#006c66", size = 0.7) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r intCon_box_adults}
box_intCon_adults <- box_intCon %>% 
  filter(sample == "adults") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r retest_hedge_data}
# take data of first reli day for internal consistency
hedge_retest <- reli %>% 
  filter(studyversion == "hedge") %>% 
  group_by(subjID, reliday, sample) %>% 
  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)

@@

```{r retest_hedge_kids}
hedge_retest_kids <- hedge_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "#006c66", size = 0.7) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

```{r retest_hedge_adults}
hedge_retest_adults <- hedge_retest %>% 
  filter(sample == "adults") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 2, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

```{r retest_box_data}
# take data of first reli day for internal consistency
box_retest <- reli %>% 
  filter(studyversion == "box") %>% 
  group_by(subjID, reliday, sample) %>% 
  tidyboot_mean(column = correctBox, na.rm = TRUE)

@@

# summary
psych::describeBy(box_retest, box_retest$sample)
```
```{r retest_box_kids}
box_retest_kids <- box_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "#006c66", size = 0.7) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

```{r retest_box_adults}
box_retest_adults <- box_retest %>% 
  filter(sample == "adults") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Testday 1", y = "Testday 2")

>>>>

```{r variation_hedge_plot}
tmp <- variationHedgeInd

variationHedgeInd <- variationHedgeInd %>% 
  mutate(
    ageInYears = factor(ageInYears, levels = c("3", "4", "5", "18"))
  )

hedge_variation_plot <- ggplot() +
  # child data
  geom_smooth(
    data = variationHedgeInd %>% filter(sample == "kids"),  
    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
    method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey",
  ) +

@@

  # scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
  scale_shape_manual(values = c(16, 18)) + 
  scale_alpha_discrete(range = c(1, 0.4)) + 
  scale_linetype_manual(values = c("solid", "dashed")) +

  # adult data
  geom_jitter(
    data = variationHedgeInd %>% filter(sample == "adults"), 
    aes(x = 6.5, y = mean, col = as.factor(ageInYears), shape = datacollection), alpha = 0.8, width = .05, height = .01,  
  ) +

@@

  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age group", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) +

@@

```{r intCon_hedge_data}
# take data of first reli day for internal consistency
hedge_intCon <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample, ageInYears) %>%
  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)

@@

```{r intCon_hedge_kids}
hedge_intCon_kids <- hedge_intCon %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 5, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r intCon_hedge_adults}
hedge_intCon_adults <- hedge_intCon %>% 
  filter(sample == "adults") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 2, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r intCon_box_data}
# take data of first reli day for internal consistency
box_intCon <- reli %>% 
  filter(studyversion == "box" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample, ageInYears) %>%
  tidyboot_mean(column = correctBox, na.rm = TRUE)

@@

```{r intCon_box_kids}
box_intCon_kids <- box_intCon %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r intCon_box_adults}
box_intCon_adults <- box_intCon %>% 
  filter(sample == "adults") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r retest_hedge_data}
# take data of first reli day for internal consistency
hedge_retest <- reli %>% 
  filter(studyversion == "hedge") %>% 
  group_by(subjID, reliday, sample, ageInYears) %>% 
  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)

@@

```{r retest_hedge_kids}
hedge_retest_kids <- hedge_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

```{r retest_hedge_adults}
hedge_retest_adults <- hedge_retest %>% 
  filter(sample == "adults") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 2, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

```{r retest_box_data}
# take data of first reli day for internal consistency
box_retest <- reli %>% 
  filter(studyversion == "box") %>% 
  group_by(subjID, reliday, sample, ageInYears) %>% 
  tidyboot_mean(column = correctBox, na.rm = TRUE)

@@

# summary
psych::describeBy(box_retest, box_retest$sample)
```
```{r retest_box_kids}
box_retest_kids <- box_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

```{r retest_box_adults}
box_retest_adults <- box_retest %>% 
  filter(sample == "adults") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Testday 1", y = "Testday 2")
